### 2020-05-16 paper.tex
Reactive Inspector
RxFiddle

Salvaneschi et al. did focus their research heavily on RP during the mid 2010s. Beside the creation of REScala in 2014 \cite{REScala}, an RP DSL and runtime for the Scala programming language, they looked into the debugging habits of software engineers as well. In the paper ``Debugging for Reactive Programming'' \cite{positiveEffectsRP}, Salvaneschi et al. elaborate on the necessity of RP debugging tools which can understand the specific language abstractions. With the plugin \emph{Reactive Inspector} \footnote{\url{http://guidosalva.github.io/reactive-inspector/}} for the Eclipse IDE, they provide a debugger which understands the RP language abstractions of REScala. One of its main features is the visualization of the internal dependency graph. The new class of  breakpoints, the ``reactive breakpoints'', builds upon the visualized graph as well: They do not depend on a specific line of code or statement rather then on a specific node in the graph. The execution of the program can be interrupted e.g. once a node retains a specific output value or an event of interest takes place in the runtime. Along with the RP specific debugging features, \emph{Reactive Inspector} implements omniscient debugging concepts as well: Time travel allows to record and replay runtime behavior at any time.

\begin{itemize}
	\item Visualization of the graph
	\item Omniscient

Herman Benken \cite{rxfiddle}

>>>>

Salvaneschi et al. did focus their research heavily on RP during the mid 2010s. Beside the creation of REScala in 2014 \cite{REScala}, an RP DSL and runtime for the Scala programming language, they looked into the debugging habits of software engineers as well. In the paper ``Debugging for Reactive Programming'' \cite{positiveEffectsRP}, Salvaneschi et al. elaborate on the necessity of RP debugging tools which can understand the specific language abstractions. With the plugin \emph{Reactive Inspector} \footnote{\url{http://guidosalva.github.io/reactive-inspector/}} for the Eclipse IDE, they provide a debugger which understands the RP language abstractions of REScala. One of its main features is the visualization of the internal dependency graph. The new class of  breakpoints, the ``reactive breakpoints'', builds upon the visualized graph as well: They do not depend on a specific line of code or statement rather then on a specific node in the graph. The execution of the program can be interrupted e.g. once a node retains a specific output value or an event of interest takes place in the runtime. Along with the RP specific debugging features, \emph{Reactive Inspector} implements omniscient debugging concepts as well: Time travel allows to record and replay runtime behavior at a later time without reexecution.

\subsection{rxfiddle}

\emph{rxfiddle} proposed by Banken et al. is the first reference implementation of their RP debugger architecture for the ReactiveX API specification described in their paper ``Debugging Data Flows in Reactive Programs'' \cite{rxfiddle}. The design defines two independent parts: The (i) \emph{Host instrumentation} instruments a ReactiveX implementation to emit events at runtime (e.g. when an \mintinline{TypeScript}{Observable} is created or subscribed) which get collected. The (ii) \emph{Visualizer} component interprets these events and presents them along two dimensions: The StoryFlow graph \cite{storyflow} shows when an \mintinline{TypeScript}{Observable} is created and how it interacts with other \mintinline{TypeScript}{Observable}s. An additional marble diagram\footnote{Marble diagrams are used in the ReactiveX community to describe the behavior of an \mintinline{TypeScript}{Observable} over its life time. They are considered valuable for documentation \cite{marblediagrams} as well as for testing \cite{marbletesting}} for every \mintinline{TypeScript}{Observable} is used to display the values it emits over time.

The reference implementation supports event collection for RxJS-based code in version 4 and 5. It can either be used on a local development machine on existing projects or by copying code snippets to the online available.
